### 2020-08-14 manuscript/manuscript.rmd
added legend and refined figure

```{r n_cat, fig.width=6, fig.height=12}

@@

# Generate plots
gg_rank_phil = 
  pb_summaries %>% 
  filter( matrix=="Philippe2009" ) %>%
  ggplot() +
  geom_line(aes(x=rank, y=count, col=model)) + 
  theme(legend.position="right")

gg_rank_whel = 
  pb_summaries %>% 
  filter( matrix=="Whelan2017_strict" ) %>%
  ggplot() +
  geom_line(aes(x=rank, y=count, col=model)) + 
  theme(legend.position="right")

gg_mds_phil = 
 pb_summaries %>% 
  filter( matrix=="Philippe2009" ) %>% 
  ggplot() +
  geom_point(aes(x=x_global, y=y_global, size=count, col=model), alpha=0.4 ) + 
  theme(legend.position="right")

gg_mds_whel = 
 pb_summaries %>% 
  filter( matrix=="Whelan2017_strict" ) %>% 
  ggplot() +
  geom_point(aes(x=x_global, y=y_global, size=count, col=model), alpha=0.4 ) +  
  theme(legend.position="right")

@@

```{r n_cat_render, fig.width=6, fig.height=12}

@@

**Extended Data Fig. 3.5** The impact of adding a large number of categories.

>>>>

```{r n_cat }

@@

# Generate plots
gg_rank_phil = 
  pb_summaries %>% 
  filter( matrix=="Philippe2009" ) %>%
  ggplot() +
  geom_line(aes(x=rank, y=count, col=model)) + 
  xlab( "category rank" ) +
  ylab( "site count" ) +
  theme(legend.position="right")

gg_rank_whel = 
  pb_summaries %>% 
  filter( matrix=="Whelan2017_strict" ) %>%
  ggplot() +
  geom_line(aes(x=rank, y=count, col=model)) + 
  xlab( "category rank" ) +
  ylab( "site count" ) +
  theme(legend.position="right")

gg_mds_phil = 
 pb_summaries %>% 
  filter( matrix=="Philippe2009" ) %>% 
  ggplot() +
  geom_point(aes(x=x_global, y=y_global, size=count, col=model), alpha=0.4 ) + 
  xlim( -0.5, 0.5) +
  ylim( -0.6, 0.6) +
  xlab( "MDS1" ) +
  ylab( "MDS2" ) +
  theme(legend.position="right")

gg_mds_whel = 
 pb_summaries %>% 
  filter( matrix=="Whelan2017_strict" ) %>% 
  ggplot() +
  geom_point(aes(x=x_global, y=y_global, size=count, col=model), alpha=0.4 ) +  
  xlim( -0.5, 0.5) +
  ylim( -0.6, 0.6) +
  xlab( "MDS1" ) +
  ylab( "MDS2" ) +
  theme(legend.position="right")

@@

```{r n_cat_render, fig.width=6, fig.height=7}

@@

**Extended Data Fig. 3.5** The allocation of frequency categories across sites in the Philippe2009 matrix (left column) and Whelan2017_strict matrix (right column) for the constrained Posson+nCAT60 model and unconstrained Posson+CAT models (differentiated with color). These plots are for singe sampled isolated from the end of PhyloBayes chain files. (A,B) The count of sites allocated to each equilibrium frequency category, with the categories ranked from the most abundand to least abundant along the x axis. The unconstrained CAT analyses have a long tale categories that are allocated to very few sites, which adds a considerable number of parameters that pertain to only a small fraction of the data. The nCAT60 analyses, which are constrained to 60 sites, have no such long tail and the rarest categories are allocated to a far greater number of sites than any of the sites in the long tail of the CAT analyses. (C,D) MDS plots for the amino acid frequencies. Each point is for a single category, the area of the point is proportional to the number of sites allocated to that category, and categories with closer points have more similar amino acid frequencies. A single MDS analysis was done for all analyses, so that the projections are the same in each plot. For both matrices, the much larger number of categories in the unconstrained CAT analyses laregely subdivide the amino acid frequency space already covered in the constrained nCAT60 analyses, and just subdivide that space into a far greater number of rare categories. This adds a considerable number of parameters for describing a similar overall space.
